---
title: "Data Wrangling"
author: "Bastola"
date: "`r format(Sys.Date(), ' %B %d %Y')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      collapse = TRUE, 
                      comment=NA, 
                      warning = FALSE,
                      message = FALSE,
                      fig.height = 4, fig.width = 6, fig.align='center')


library(dplyr)
library(dslabs)
library(ggplot2)
library(ggthemes)
library(tidyverse)
library(dslabs)
library(datasauRus)
```



```{r}
library(babynames)
knitr::kable(head(babynames), type = "html")
```

## Your Turn 1

Which of these is NOT a way to select the `name` and `n` columns together?


```{r}
select(babynames, -c(year, sex, prop))
select(babynames, name:n)
select(babynames, starts_with("n"))
select(babynames, ends_with("n"))
```


*Answer:*


## Your Turn 2

Use filter() with the logical operators to extract:

### a. All of the names where prop is greater than or equal to 0.08

```{r}

```

### b. All of the babies named "Rose"

```{r}

```


### c. All of the names that have a missing value for n

```{r}

```


## Your Turn 3

Use the codes mentioned so far to compute three statistics:

- the total number of children who ever had your name
- the maximum number of children given your name in a single year
- the mean number of children given your name per year


```{r}


```

## Your Turn 4

Use Boolean operators to alter the code below to return only the rows that contain:

### a. Girls named Rhea

```{r}

```


### b. Names that were used by exactly 5 or 6 children in 1990

```{r}


```


### c. Names that are one of Apple, Yoroi, Ada

```{r}

```

## Your Turn 5

Find the year your first name is most common.

```{r}


```

## Your Turn 6

### a. Use min_rank() and mutate() to rank each row in babynames from largest prop to smallest prop.

```{r}

```


### b. Compute each name's rank within its year and sex.

```{r}

```


### c. Then compute the median rank for each combination of name and sex, and arrange the results from highest median rank to lowest.


```{r}


```


